Generating Performance Improvement Suggestions by using Cross-Organizational Process Mining

### 2015-11-21 4_methodology/methodology.tex
no message

This stage of methodology can be visualized as an input-output system in Figure~\ref{fig:performance-indicator-clustering-blackbox}. 
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/performance-indicator-clustering-blackbox}
  \caption{Performance Indicator Clustering Stage as Black-box }
  \label{fig:performance-indicator-clustering-blackbox}
\end{figure}

@@

Algorithm of recommendation generation function is based on the idea of checking other clusters for a significant change in performance indicators, where significance is defined by the threshold provided by user. After finding significant difference, all organizations in other clusters are checked against mismatch patterns with the starting and ending activities defined in performance indicators. Only mismatches which are located between the activities that causes high level of difference in performance indicators are analyzed. This approach is formalized in Algorithm~\ref{algo:recgen}.
 \begin{algorithm}
\DontPrintSemicolon % Some LaTeX compilers require you to use \dontprintsemicolon instead 
\KwIn{$O$ organization, $C$ Cluster Analysis Data, $P$ performance difference threshold}
\KwOut{$Recommendations$ a set of recommendations}
$Recommendations \leftarrow \{\}$ \;
$i \leftarrow C(Assignments(O))$ \;
\For{$Centroid \in C(Cluster Centroids_{i})$} { 
  \For{$Centroid' \in C(Cluster Centroids_{j})\ i\neq j$} { 
    \If{$Centroid(A_{start}) = Centroid'(A_{start})\ \&\ Centroid(A_{end}) = Centroid'(A_{end})$} {
      \If{ ($\left |  Centroid(Value) -  Centroid'(Value)\right | \div Centroid(Value)) \geq P$  } {
        $A_{start} \leftarrow Centroid(A_{start})$ \;
        $A_{end} \leftarrow Centroid(A_{end})$ \;
        $MismatchPatterns \leftarrow \{\}$ \;
        \For{$O' \in C(Assignments(j))$} {
          $MismatchPatterns$ \leftarrow  Mismatch Pattern Analysis($O$,$O'$,$A_{start}$,$A_{end}$) \;
        }
        $Recommendations$ \leftarrow  Recommendation($O$,$A_{start}$,$A_{end}$, $MismatchPatterns$) \;
      }
    }
  }
}
\Return{$Recommendations$} \;
\caption{Recommendation Generation}
\label{algo:recgen}
\end{algorithm}
This stage of methodology can be visualized as gathering inputs of mismatch patterns data and cluster analysis data in Figure~\ref{fig:recommendation-generation-blackox}.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/recommendation-generation-blackbox}
  \caption{Recommendation Generation Stage as Black-box}
  \label{fig:recommendation-generation-blackox}
\end{figure}

>>>>

@@

Algorithm of recommendation generation function is based on the idea of checking other clusters for a significant change in performance indicators, where significance is defined by the threshold provided by user. After finding significant difference, all organizations in other clusters are checked against mismatch patterns with the starting and ending activities defined in performance indicators. Only mismatches which are located between the activities that causes high level of difference in performance indicators are analyzed. This approach is formalized in Algorithm~\ref{algo:recgen}.
 \begin{algorithm}
\DontPrintSemicolon % Some LaTeX compilers require you to use \dontprintsemicolon instead 
\KwIn{$O$ organization, $C$ Cluster Analysis Data, $P$ performance difference threshold}
\KwOut{$Recommendations$ a set of recommendations}
$Recommendations \leftarrow \{\}$ \;
$i \leftarrow C(Assignments(O))$ \;
\For{$Centroid \in C(Cluster Centroids_{i})$} { 
  \For{$Centroid' \in C(Cluster Centroids_{j})\ i\neq j$} { 
    \If{$Centroid(A_{start}) = Centroid'(A_{start})\ \&\ Centroid(A_{end}) = Centroid'(A_{end})$} {
      \If{ ($\left |  Centroid(Value) -  Centroid'(Value)\right | \div Centroid(Value)) \geq P$  } {
        $A_{start} \leftarrow Centroid(A_{start})$ \;
        $A_{end} \leftarrow Centroid(A_{end})$ \;
        $MismatchPatterns \leftarrow \{\}$ \;
        \For{$O' \in C(Assignments(j))$} {
          $MismatchPatterns$ \leftarrow  Mismatch Pattern Analysis($O$,$O'$,$A_{start}$,$A_{end}$) \;
        }
        $Recommendations$ \leftarrow  Recommendation($O$,$A_{start}$,$A_{end}$, $MismatchPatterns$) \;
      }
    }
  }
}
\Return{$Recommendations$} \;
\caption{Recommendation Generation}
\label{algo:recgen}
\end{algorithm}
